\section{Architectural Patterns}

TODO:

\subsection{Entity-Component-System}\label{ssection:ecs}

Used in physic engines, and when there are a lot of things to handle.

% CHANGED: not used too much in UI
% In UI Systems as there are also lots of things to handle. UI widgets do not necessary need to interact with other UI widgets. So using this architecture enables performance optimizations.

Other examples include making certain objects in the physics engine adopt a characteristic: i.e. solid/has collision, soft body/hard body, and other physics-aware components.\bs
\\
It could be argued that a ``controllable'' component could exist to make certain object player-controllable (i.e player characters, car, etc.).\bs
\\
Objects could also inherit components that made them aware of inputs such as mouse. Before Frostbite uses input trees and hit-zone entities, certain UI element could attach mouse interaction components to make them respond to mouse events such as hover, enter and leaving hitzones, click, etc.\bs
\\

Update calls can be queued for all objects at once. Update states can be cached. Cached data are much faster.

\subsubsection{Composition over Inheritance}

TODO:
OOP principle that makes inheritance based on composition / behavior rather than inheritance from parent.
\bs
Consider code in section \ref{code:coi-component}, rather than defining class by their ``likeness'', we define it by its function.
\bs
Then in 

\subsection{Model-View-Controller}

TODO: Mostly used in UI development. 