% Set page numbering to roman for preface
\pagenumbering{roman}

\section*{Preface \& Foreword}
\addcontentsline{toc}{section}{Preface \& Foreword}

% !!! Purpose
\subsection*{Purpose}
\addcontentsline{toc}{subsection}{Purpose}

The purpose of this report is to explore and observer different kinds of theoretical methods nad patterns and how they're used ot develop components that make up a game.\bs
\\
There exists a discrepancy of knowledge acquired in school versus ones learned in the company. Mainly, because of my areas of studies is in electrical engineering, discussions involving software development, software structure, and methodologies are minimal, if not non-existent. Therefore this exploration and report is an excellent opportunity to broaden my perspective in software development.\bs
\\
As well to consolidate my knowledge as a whole in the industry as design patterns are software development concepts and potentially applicable elsewhere in the tech industry.

% !!! Background
\subsection*{Background}
\addcontentsline{toc}{subsection}{Background}

This report is produced during the second and third co-op term while working for Electronic Arts (EA)'s division in Edmonton. The studio name is BioWare which produces games with rich single player stories. The technology worked with is shared across many EA studios for various franchises and licenses. My position at Bioware is an \textit{associate developer (programmer)} for the game Anthem, set to release in late Feburary of 2019. Modern EA games are built on the game engine called Frostbite. My contribution is mainly to the game client's code as well as the engine codebase.

% !!! Scope
\subsection*{Scope of Coverage}
\addcontentsline{toc}{subsection}{Scope of Coverage}

The report will cover most of the original design patterns as defined by the book ``Gang of Four''\cite{gof}. Many of the patterns will not be discussed in too much detail as they might not apply. Technical content of the report, including code, diagrams, and models will be general and high level. Any detailed breakdown, explanation, and specification of a existing idea or technology in this report is not confidential or proprietary. This report will not cover any confidential or proprietary data such as code used in the game Anthem or Frostbite as it is a property of EA or BioWare.\bs
\\
The technical coverage cited in this report is limited because the co-op work term position is working in UI/UX. Thus I lack understanding in other areas of the game such as character handling, world rendering, etc. Many of the workflows I describe in this report may only apply to UI/UX development within this project. BioWare, the studio for developming games focuses more on stories and game content rather than research of new and groundbreaking design patterns for games, thus the software methods, patterns, and provided sample code are industry generic and does not expose any confidential information.\bs
\\
As the scope of game development or software development extends wide in breadth, this report will not thoroughly cover topics of object oriented programming, development methodologies, specific syntax in a programming language, specific implementations of algorithms in a programming language, and psychology of UI/UX. 

% !!! (Other) Contributors
\subsection*{Contributors}
\addcontentsline{toc}{subsection}{Contributors}

Other contributors to this report is as follows:

\begin{itemize}
	\item \textbf{Gibson, Tim} (Senior Software Lead, manager) contribution by supervising my workfly and giving advice on how design patterns are applied in BioWare games, EA Frostbite, and how they can be used outside of games.\\
	\item \textbf{Johnson, Chris} (Software Engineer, supervisor, manager) contribution by helping me working through Anthem UI/UX projects as Chris is expert in UI programming. Chris Johnson also gave how some of the design patterns work in UI in context. Finally, Chris Johnson oversees my work term and report and provided valuable feedback.
\end{itemize}
